---
title: "EDS 221 Day 4 Interactive"
format: html
editor: visual
---

## Functions

Make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(my_dollars = 10.13)
```

```{r}
# gives the same as above, don't have to label argument if you know the order
double_value(10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}
convert_f_to_c <- function(temp_f) {
  print((5 / 9) * (temp_f - 32))
}

convert_f_to_c(temp_f = 70) # good practice to refer to arguments by name
```

Create a function that given inputs of age and hometown returns "I am \_\_ years old, and I'm from \_\_\_"

```{r}
about_me <- function(age_yr, hometown) {
  print(paste("I am", age_yr, "years old, and I'm from", hometown))
 }

about_me(age_yr = 23, hometown = "Santa Barbara")
```

```{r}
double_value2 <- function(dollars) {
  dollars * 2
}
```

```{r}
double_value2(dollars = 10) * 0.08
```

Print and return statements

Print: "show me"

return: "store this so i can use it later"
